---
title: "Metric backbone"
author: "Jonathan Bourne"
date: "27 September 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

Stage 1: Identify lines that are definately semi-metric
Stage 2: Identify lines that are definately 2 hop metric
Stage 3: Identify remaining lines with breadth first search
#Phase 1
```{r}
#stage 1 
Phase1SemiMetricRemoval <- function(s){
#Matrix of 1 triangle semi-metric edges
  #s: a distance matrix
      Smat <- col(s) 
      
      SemiMetric <- 1:ncol(s) %>%
      map(~{
       print(.x)
        TargetRows <- .x:ncol(s)
        LogicMat <- s[TargetRows,TargetRows, drop = F] + 
          s[TargetRows,.x][Smat[1:length(TargetRows),1:length(TargetRows)]]  < s[TargetRows,.x]
       
        
        matrix(data = c(rep(NA, .x-1),rowSums(LogicMat, na.rm = TRUE ) > 0), ncol = 1) #TRUE means semi-metric edge
      
      }) %>%
      do.call(cbind,.)
  
      SemiMetric[upper.tri(SemiMetric)]  <- t(SemiMetric)[upper.tri(SemiMetric)]
      
      s[SemiMetric] <- NA #change Semi-metric values to NA. This makes the further stages easier to manage
    
    s

}


Phase1SemiMetricRemoval2 <- function(s){
#Matrix of 1 triangle semi-metric edges
  #s: a distance matrix
      Smat<- col(s) 
      
      SemiMetric <- 1:ncol(s) %>%
      map(~{
        #print(.x)

     LogicMat <- s + s[,.x][Smat] < (s[,.x]) #slightly faster than using transpose it still takes ages though
 
     matrix(data = rowSums(LogicMat, na.rm = TRUE ) > 0, ncol = 1) #TRUE means semi-metric edge
      
      }) %>%
      do.call(cbind,.)
    
    
    s[SemiMetric] <- NA #change Semi-metric values to NA. This makes the further stages easier to manage
    
    s

}


Phase1SemiMetricRemovalfor <- function(s){
#Matrix of 1 triangle semi-metric edges
  #s: a distance matrix
      Smat <- col(s) 
      SemiMetric <- matrix(FALSE, ncol = ncol(s), nrow = ncol(s))
      
      for(.x in 1:ncol(s)){
     #   print(.x)
        TargetRows <- .x:ncol(s)
        LogicMat <- s[TargetRows,TargetRows, drop = F] + 
          s[TargetRows,.x][Smat[1:length(TargetRows),1:length(TargetRows)]]  < s[TargetRows,.x]
       
       SemiMetric[.x,TargetRows] <- rowSums(LogicMat, na.rm = TRUE ) > 0 #TRUE means semi-metric edge
      
      }
  
      SemiMetric[lower.tri(SemiMetric)]  <- SemiMetric[upper.tri(SemiMetric)]
      
      s[SemiMetric] <- NA #change Semi-metric values to NA. This makes the further stages easier to manage
    
    s

}


txt <- 'arma::mat S = Rcpp::as< arma::mat >(s);
const int n -> S.n_rows;
//arma::mat Smat = n;
vector<unsigned> Out;
 for (int i=1; i < n; ++i) {
 vec TargetRows = linspace<vec>(0, i, i + 1); 
  Out[i] = arma::accu(TargetRows);

 }
return Out;'

Rcpp::cppFunction(depends = "RcppArmadillo", code = '
Rcpp::List Phase1cpp(const arma::mat &s) {
  const int n = s.n_rows;
  vec x(10);
vec y = zeros<vec>(10);

  for (int i=1; i < n; ++i) {
  vec TargetRows = linspace<vec>(0, i, i + 1); 
  Out[i] = arma::accu(TargetRows);

 }
 return Rcpp::List::create( Rcpp::Named("Out") = Out,
Rcpp::Named("Out") = n );
}')

Phase1cpp(matrix(rnorm(25), ncol = 5))

library(RcppArmadillo)

Rcpp::cppFunction(depends = "RcppArmadillo", code = '
Rcpp::List Phase1cpp(const arma::mat &X, const arma::mat &Y) {
   const int n = X.n_rows;
 return Rcpp::List::create( Rcpp::Named("Out") = (X<Y),
Rcpp::Named("Out") = n );
}')



txt <- 'arma::mat Am = Rcpp::as< arma::mat >(A);
arma::mat Cm = Rcpp::as< arma::mat >(C);
arma::mat B = inv(trans(Am) * Cm * Am);
arma::mat PTDF = Cm * Am * B;
return Rcpp::List::create( Rcpp::Named("Imp") = B ,
                           Rcpp::Named("PTDF") = PTDF ) ; '

flowCalcCpp <- cxxfunction(signature(A="numeric",
C="numeric"),
body=txt,
plugin="RcppArmadillo")

```


#Phase 2
```{r}

Phase2 <- function(s3){
  #This function postively identifies metric edges. It is the second phase of finding the metric backbone.
  #s3 the weighted adjacncy matrix, this should already have had triangles removed by phase 1 one the metric back bone
  
  #Create a logical matrix, where TRUE means the edge is metric
  MetricDF <- matrix(FALSE, ncol = ncol(s3), nrow = nrow(s3))
  
    for(n in 1:ncol(s3)){  #for each node in the graph
  print(n)    
      SourceNode <- n
      
      #Finds shortest edge of that node
      ShortestEdgeID <- which.min(s3[,SourceNode])
      #Makes shortest edge metric in the matrix
      MetricDF[ShortestEdgeID,SourceNode]<-MetricDF[SourceNode,ShortestEdgeID] <- TRUE
      #Identifies all the metric edges attached to this node
      MetricVect <- which(MetricDF[,SourceNode]==T)
     
      #find shortest two hop distance using each of the metric edges
      Min_to_beat <- MetricVect %>%
        map_dbl(~Shortest2Hop(s3, SourceNode, .x)) %>% min
      
      SVESN <- s3[!MetricDF[,c(SourceNode)], SourceNode] #Source Vector Excluding Source Node
      #Sort edges by ascending distance
      OrderedEdgeDistance <- sort(SVESN) 
      
      p <- 1
      while(OrderedEdgeDistance[p] < Min_to_beat & p <= length(OrderedEdgeDistance)){ 
        #Find Index of new metric edge
        NewMetricEdge <- which(colnames(s3)==names(OrderedEdgeDistance[p]))
        #Update Min_to_beat if necessary
        #Min_to_beat <- c(Shortest2Hop(s3, SourceNode, NewMetricEdge), Min_to_beat) %>% min 
        print(paste("p is ", p, "Min to beat is",Min_to_beat))
        #Create new metric entry
        MetricDF[NewMetricEdge, SourceNode] <- MetricDF[SourceNode, NewMetricEdge] <-TRUE
        p <- p+1

    } 
  #return the Metric edge Logical matrix    

    }
  
    return(MetricDF)
}


Shortest2Hop <- function(AdjacencyMat, SourceNode, TargetNode){
  #This function finds the shortest two hop distance starting from a named node and going through a second node.
  #The weighted adjacency matrix of the graph
  #SourceNode start point of the path search
  #TargetNode: A node 1 hop from the source node it is the middle of the path
      
      MetricLength <- AdjacencyMat[SourceNode, TargetNode] #Length of metric edge
  
      #The minimum length edge in the node at the other end of the metric edge, this excludes the metric edge itself
      MinLength <-min(s3[, TargetNode][-SourceNode], na.rm = TRUE) 
      
      #Return the shortest two hop distance from the Source Node via Node at other end of metric edge
      MinLength + MetricLength 
      }

```

#Phase 3
https://github.com/igraph/igraph/blob/c517ad26e537bbdf363a1f6f9cabd66040664fdd/src/structural_properties.c#L4214

4214 t0 4390

```{r}
MakeEdgList <- function(mat, VarName){
  #required as part of the phase 3 function
  
  melts3 <- mat*lower.tri(mat)
  melts3[ melts3 == 0 ] <- NA
  melts3 <- melts3 %>% 
    as.data.table(., keep.rownames= T) %>%
    melt(id.vars = "rn", 
       variable.name = "node2", 
       value = VarName, 
       na.rm = T)
  
}


Phase3MetricEdges <- function(s3, s4){
  #Removes the final semi-metric edges creating the metric backbone
  
  #variables throughout the function to save memory
  
  melts3 <- MakeEdgList(s3, "weight")
  melts4 <- MakeEdgList(s4, "Metric")

melts3 <- melts4[melts3, on = c("node2", "rn")][!is.na(weight)] %>%
  as.tibble %>% rename(node1 = rn) %>%
  mutate(edge_name = paste0(node1,"_", node2),
         Metric = ifelse(is.na(Metric), FALSE, TRUE),
         node2 = as.character(node2))

rm(melts4)

g <- graph_from_data_frame(melts3, directed = FALSE)

VertexID<- tibble(node = get.vertex.attribute(g, "name"), ID = 1:vcount(g))

Unlabled <- melts3 %>%
  filter(Metric ==FALSE) %>%
  left_join(., VertexID, by = c("node1" = "node")) %>%
  left_join(., VertexID, by = c("node2" = "node")) %>%
  rename(node1_ID = ID.x, node2_ID = ID.y)

rm(VertexID)

print("Perform Breadth first search across all unlabled nodes")

ShortestPath <-1:nrow(Unlabled) %>% map_dbl(~{
  print(paste(.x, "of", nrow(Unlabled)))
  distances(g, v = Unlabled$node1_ID[.x], to =Unlabled$node2_ID[.x] )
  })

Unlabled <- Unlabled %>%
  mutate(TrueShortest = ShortestPath,
         Metric = ifelse(all.equal(weight,TrueShortest), TRUE, FALSE))

print("Remove final Semi-metric edges")

melts3 <- melts3 %>%
  filter(Metric) %>%
  bind_rows(select(Unlabled, node1:edge_name))
  
return(melts3)

}

```

#Saved calcs

```{r}
SavedCalcs <- function(n){
  (2*n+1)*(n+1)/(6*n^2)
  
}


SavedCalcs(4000)

```


```{r}
library(compiler)

Phase1forcmp <- cmpfun(Phase1SemiMetricRemovalfor)


microbenchmark(Phase1SemiMetricRemoval(s), 
               Phase1SemiMetricRemoval2(s), 
               Phase1SemiMetricRemovalfor(s),
               Phase1forcmp(s), times = 10)


microbenchmark(rowSums(LogicMat, na.rm = TRUE ) > 0, LogicMat %*% matrix(1, nrow = 1000) >0)


(LogicMat %*% matrix(1, nrow = 1000) > 0)[,1]

txt <- 'arma::mat Am = Rcpp::as< arma::mat >(A);
arma::mat Cm = Rcpp::as< arma::mat >(C);
arma::mat B = inv(trans(Am) * Cm * Am);
arma::mat PTDF = Cm * Am * B;
return Rcpp::List::create( Rcpp::Named("Imp") = B ,
                           Rcpp::Named("PTDF") = PTDF ) ; '

rowsumtxt <- "arma::mat LogicMatm = Rcpp::as< arma::mat >(LogicMat);
int r,c;
int sum_rows;
for (int i=0; i<r; i++) {
        sum_rows=0;
        for (int j=0; j<c; j++) {
            sum_rows += LogicMatm[i][j];
        }
return sum_rows"

RowsumCpp <- cxxfunction(signature(LogicMat="numeric"),
body=rowsumtxt,
plugin="RcppArmadillo")



```


```{r}

nodebase <-1000

set.seed(876)
s <- matrix(rnorm(nodebase^2), nodebase) #%>% cor
 s <- s +abs(min(s))+0.001
 s[lower.tri(s)] = t(s)[lower.tri(s)]
 diag(s) <- 0
colnames(s) <- make.names(1:ncol(s))
rownames(s) <- make.names(1:ncol(s))
 
#s <-( 1-cor(s))  #square is used to exxagerate differences for testing small matrices
# s2<- s
# s2
 
s3 <- Phase1SemiMetricRemoval(s)
s4 <- Phase1SemiMetricRemoval2(s)
diag(s3)<- NA

s4 <- Phase2TwoHopMetric(s3)
s5 <- Phase2(s3)

sum(s5[lower.tri(s5)])
sum(s4[lower.tri(s4)])
test <- Phase3MetricEdges(s3, s4)

microbenchmark(Phase1SemiMetricRemoval(s),Phase1SemiMetricRemoval2(s), times = 100)

#diag(s4) <- NA
s4[1:10,1:10]

sum(s4, na.rm = T)#number of postively ID'd metric edges

ecount(g)
maxedge <- nodebase*(nodebase-1)/2
ecount(g)/(maxedge )

table(degree(g))

clus <-cluster_louvain(g)
colors <- rainbow(max(membership(clus)))
plot(g,vertex.color=colors[membership(clus)], vertex.label=NA, vertex.size = 3)

```


#Try with real data
```{r}
 
setwd("/home/jonno/Dropbox/MScThesis/DayTimeSeries")

datdat <- readRDS(list.files()[1]) %>% 
        as.tibble 
      
      cormat <- datdat[,2:ncol(datdat)] %>%
        as.matrix %>% cor(.)
      distmat <-1-cormat
      distmat2 <- sqrt(2*(1-cormat))
      distmat3 <- distmat2*(cormat>0.7)
      diag(cormat) <- NA
      
      min(distmat)
      max(distmat)
      
Case1 <- Phase1SemiMetricRemoval(distmat)
Case2 <- Phase1SemiMetricRemoval(distmat2)
test1 <- Phase2TwoHopMetric(Case1)
test2 <- Phase2TwoHopMetric(Case2)
#test3 <- Phase3MetricEdges(test, test2)

saveRDS(Case1, file.path(SavedData, "Case1.rds"))
saveRDS(Case2, file.path(SavedData, "Case2.rds"))

Case1[is.na(Case1)] <- 0
Case2[is.na(Case2)] <- 0

 
gCase1 <- graph_from_adjacency_matrix(Case1, mode = "undirected", weighted = "weight", diag = FALSE) 
gCase2 <- graph_from_adjacency_matrix(Case2, mode = "undirected", weighted = "weight", diag = FALSE) 
gtest2 <- graph_from_adjacency_matrix(distmat2, mode = "undirected", weighted = "weight", diag = FALSE) 

saveRDS(gtest, file.path(SavedData, "gtestSemiMetric1.rds"))

#gtest<- readRDS(file.path(SavedData, "gtestSemiMetric1.rds"))

maxedgetest <- ncol(cormat)*(ncol(cormat)-1)/2

ecount(gCase1)
ecount(gCase1)/(maxedgetest)
components(gCase1)

ecount(gCase2)
ecount(gCase2)/(maxedgetest)
components(gCase2)



ecount(gtest2)
maxedgetest2 <- ncol(cormat)*(ncol(cormat)-1)/2
ecount(gtest2)/(maxedgetest2)
components(gtest2)

fc <-cluster_louvain(gCase1)
fc2 <-cluster_louvain(gtest2)

length(membership(fc))
length(membership(fc2))

test <- tibble(names = fc$names, c1 = membership(fc), c2 = membership(fc2)) %>%
  group_by(c2) %>%
  mutate(countC2 = n()) %>%
  ungroup %>%
  mutate(c22 = ifelse(countC2>20, c2, 0))

table(test$c1, test$c22)

plot(gtest2)

colors <- rainbow(max(membership(fc)))
plot(gtest,vertex.color=colors[membership(fc)], vertex.label=NA, vertex.size = 3)

```


```{r}
apply_cosine_similarity <- function(df){
  cos.sim <- function(df, ix) 
  {
    A = df[ix[1],] 
    B = df[ix[2],]
    return( sum(A*B)/sqrt(sum(A^2)*sum(B^2)) )
  }   
  n <- nrow(df) 
  cmb <- expand.grid(i=1:n, j=1:n) 
  C <- matrix(apply(cmb,1,function(cmb){ cos.sim(df, cmb) }),n,n)
  C
}



dist2<- apply_cosine_similarity(t(as.matrix(datdat[, 2:100])))
dist2 <- cor(as.matrix(datdat[, 2:100]), method = "spearman")
dist1 <- cor((as.matrix(datdat[, 2:100])))

dist1[1:10, 1:10]
dist2[1:10, 1:10]

dist2 <- (1-dist2)

dist3 <- dist2



test2 <- Phase1SemiMetricRemoval(dist2)
test2[is.na(test2)] <- 0
diag(test2) <- 0

orderedheat(test2, order = "both", simMat = T, mergey = 1, mergex = 1, xblocks=1, yblocks=1)

gtest <- graph_from_adjacency_matrix(test2 , mode = "undirected", weighted = "weight", diag = FALSE) 


ecount(gtest)
maxedgetest <- ncol(dist2)*(ncol(dist2)-1)/2
ecount(gtest)/(maxedgetest)
components(gtest)
plot(gtest)
```


Find triangles with shorter edges

I am tring to find triangles in a distance matrix where a direct path is longer than going via another point.
The function works well for low values of n but is slow for larger values. 
I am trying to find out how to speed up this process. I have tried to use lineprof an click through to lower functions, but I don't understand what it is telling me. I don't know if there is some function in igraph that would help?

```{r}
library(purrr);library(magrittr); library(lineprof);library(shiny)

RemoveTri <- function(s){
      Smat<- col(s) 
      
      RemoveEdge <- 1:ncol(s) %>%
      map(~{
      print(.x)
        
        LogicMat <- s + s[,.x][Smat] < (s[,.x]) #I used this method to avoid transposing
        matrix(data = rowSums(LogicMat, na.rm = TRUE ) > 0, ncol = 1) #TRUE means edge can be removed
      
      }) %>%
      do.call(cbind,.)
    
    
    s[RemoveEdge] <- NA
    
    s

}

CreateData <- function(n, seed){
  set.seed(seed)
  s <- matrix(rnorm(n^2), n) #%>% cor
  s <- s +abs(min(s))+0.001
  s[lower.tri(s)] = t(s)[lower.tri(s)]
  diag(s) <- 0
  return(s)
 }


s <- CreateData(100, 876)
RemoveTri(s)

s2 <- CreateData(4000, 876)
RemoveTri(s2)


l <- lineprof(RemoveTri(s))
shine(l)


```


##test symmetric creation
```{r}
library(Rcpp)

cppFunction('NumericMatrix Mat2Sym(NumericMatrix A, bool up2lo, int bf) {

  IntegerVector dim = A.attr("dim");
  size_t n = (size_t)dim[0], m = (size_t)dim[1];
  if (n != m) stop("A is not a square matrix!");

  /* use pointers */
  size_t j, i, jj, ni, nj;
  double *A_jj, *A_ij, *A_ji, *col, *row, *end;

  /* cache blocking factor */
  size_t b = (size_t)bf;

  /* copy lower triangular to upper triangular; cache blocking applied */
  for (j = 0; j < n; j += b) {
    nj = n - j; if (nj > b) nj = b;
    /* diagonal block has size nj x nj */
    A_jj = &A(j, j);
    for (jj = nj - 1; jj > 0; jj--, A_jj += n + 1) {
      /* copy a column segment to a row segment (or vise versa) */
      col = A_jj + 1; row = A_jj + n;
      for (end = col + jj; col < end; col++, row += n) {
        if (up2lo) *col = *row; else *row = *col;
        }
      }
    /* off-diagonal blocks */
    for (i = j + nj; i < n; i += b) {
      ni = n - i; if (ni > b) ni = b;
      /* off-diagonal block has size ni x nj */
      A_ij = &A(i, j); A_ji = &A(j, i);
      for (jj = 0; jj < nj; jj++) {
        /* copy a column segment to a row segment (or vise versa) */
        col = A_ij + jj * n; row = A_ji + jj;
        for (end = col + ni; col < end; col++, row += n) {
          if (up2lo) *col = *row; else *row = *col;
          }
        }
      }
    }

  return A;
  }')

s <- CreateData(1000, 876)

     Smat <- col(s) 
      
      SemiMetric <- 1:ncol(s) %>%
      map(~{
        print(.x)
        TargetRows <- .x:ncol(s)
        LogicMat <- s[TargetRows,TargetRows, drop = F] + s[TargetRows,.x][Smat[1:length(TargetRows),1:length(TargetRows)]]  < s[TargetRows,.x]
       
        
        matrix(data = c(rep(FALSE, .x-1),rowSums(LogicMat, na.rm = TRUE ) > 0), ncol = 1) #TRUE means semi-metric edge
      
      }) %>%
      do.call(cbind,.)
      
A <- SemiMetric      

test <- A +t(A)


D <- Mat2Sym(A + 0, up2lo = TRUE, 128)

microbenchmark(A+t(A), Mat2Sym(A, up2lo = FALSE, 128))

```


#compile function

```{r}
library(compiler)

s <- CreateData(100, 876)

MatWalk <- function(s){      
  Smat <- col(s) 
      
      SemiMetric <- 1:ncol(s) %>%
      map(~{
       # print(.x)
        TargetRows <- .x:ncol(s)
        LogicMat <- s[TargetRows,TargetRows, drop = F] + s[TargetRows,.x][Smat[1:length(TargetRows),1:length(TargetRows)]]  < s[TargetRows,.x]
       
        
        matrix(data = c(rep(NA, .x-1),rowSums(LogicMat, na.rm = TRUE ) > 0), ncol = 1) #TRUE means semi-metric edge
      
      }) %>%
      do.call(cbind,.)
}

MatWalkCmp <- cmpfun(MatWalk)

MatFor <- MatWalk <- function(s){      
  Smat <- col(s) 
      
      SemiMetric <- list()
      for(i in 1:ncol(s)){
       # print(.x)
        TargetRows <- i:ncol(s)
        LogicMat <- s[TargetRows,TargetRows, drop = F] + s[TargetRows,i][Smat[1:length(TargetRows),1:length(TargetRows)]] < s[TargetRows,i]
       
        
       SemiMetric[[i]] <-  matrix(data = c(rep(NA, i-1),rowSums(LogicMat, na.rm = TRUE ) > 0), ncol = 1) #TRUE means semi-metric edge
      
      }
        
      
     # SemiMetric <- do.call(cbind,SemiMetric)
}


MatForCmp <- cmpfun(MatFor)

LogicOut <- function(s1,s2,s3){
  (s1 + s2) < s3 
}

LogicOutCmp <- cmpfun(LogicOut)

MatOp <- MatWalk <- function(s){      
  Smat <- col(s) 
      
      SemiMetric <- list()
      for(i in 1:ncol(s)){
       # print(.x)
        TargetRows <- i:ncol(s)
        s1 <- s[TargetRows,TargetRows, drop = F]
        s2 <- s[TargetRows,i][Smat[1:length(TargetRows),1:length(TargetRows)]]
        s3 <- s[TargetRows,i]
        LogicMat <- (s1 + s2) < s3 
       
        
       SemiMetric[[i]] <-  matrix(data = c(rep(NA, i-1),rowSums(LogicMat, na.rm = TRUE ) > 0), ncol = 1) #TRUE means semi-metric edge
      
      }
        
      
     # SemiMetric <- do.call(cbind,SemiMetric)
}

microbenchmark(MatWalk(s), MatWalkCmp(s), MatFor(s), MatForCmp(s))


microbenchmark(LogicOut(s1,s2,s3), LogicOutCmp(s1,s2,s3))
```



```{r}
df <- seq(-1,1,0.01) %>%
  tibble(p = .) %>%
  mutate(d1 = (1-p)/2,
         d2 = 1-(p)^2,
         d3 =  sqrt(d1^2+d2^2),
         d32 = d3^2)

test <- df %>% filter(d3>1)

df %>%
ggplot(aes(x = p, y = d3)) + geom_point()

df %>%
ggplot(aes(x = p, y = d2)) + geom_point()

df %>%
ggplot(aes(x = p, y = d1)) + geom_point()

```

